---
title: "Education"
description:
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Appointments
### University of Oxford
Postdoctoral Fellow
Department of Experimental Psychology, Oxford University, UK (Advisor: Dr. Bernhard Staresina)

### University of Pennsylvania
Postdoctoral Fellow
Department of Neurosurgery, University of Pennsylvania, PA, USA (Advisor: Dr. Brett Foster)

\newpage

# Education
### University of California, Irvine
- **Ph.D. in Cognitive Sciences** (Sep 2017 – May 2022)
  - GPA: 3.99 / 4
  - Dissertation Title: Heart-brain Interaction during NREM Sleep Drives Sleep-dependent Memory Gains. (Advisor: Dr. Sara Mednick)
  - Dissertation Committee: Dr. Julian Thayer, Dr. Bryce Mander, Dr. Susanne Jaeggi, Dr. Greg Hickok, Dr. Aaron Bornstein
  
\newpage
- **MS in Statistics** (Sep 2018 – June 2020)
  + GPA: 3.74 / 4
  
\newpage

# Pedagogical Certificates

- [**Preparing for a Faculty Career Certificate Program**](https://github.com/pinchunc/certificates/blob/main/Pin-Chun%20Chen_PFFC%20Certificate.pdf) (Summer 2021)
- [**Mentoring Excellence Program**](https://github.com/pinchunc/certificates/blob/main/Pin-Chun%20Chen_MEP%20Certificate.pdf) (Summer 2021)
- [**Cascading Mentorship Certificate**](https://github.com/pinchunc/certificates/blob/main/Chen_signed.pdf) (March – June 2021)
- [**Public Speaking Certificate**](https://github.com/pinchunc/certificates/blob/main/Public%20Speaking%20Certificate%20-%20Pin-Chun%20Chen.pdf) (Jan – March 2021)
- **DTEI Certificate in Teaching Excellence Program** (Jul – Nov 2020)
- [**DTEI Course Design Certification Program**](https://raw.githubusercontent.com/pinchunc/certificates/013665983e1a91defe6ad0d849e24c195d680b8d/CDCP.pdf) (Aug 2020)
- [**DTEI Certificate in Remote Instruction**](https://raw.githubusercontent.com/pinchunc/certificates/013665983e1a91defe6ad0d849e24c195d680b8d/CRI.pdf) (July - Aug 2020) 



```{r out.width = "60%"}
#knitr::include_graphics(here::here("img/CRI.pdf"))
```


\newpage
\newpage

### National Chengchi University
- **B.S. in Psychology** (Sep 2013 – July 2017)
  + GPA: 4 / 4
- **B.Ed. in Education** (Sep 2013 – July 2017)
  + GPA: 4 / 4
