---
title: "Education"
description:
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Appointments
### University of Oxford
Postdoctoral Fellow
Department of Experimental Psychology, Oxford University, UK (Advisor: Dr. Bernhard Staresina)

### University of Pennsylvania
Postdoctoral Fellow
Department of Neurosurgery, University of Pennsylvania, PA, USA (Advisor: Dr. Brett Foster)

\newpage

# Education
### University of California, Irvine
- **Ph.D. in Cognitive Sciences** (Sep 2017 – May 2022)
  - GPA: 3.99 / 4
  - Dissertation Title: Heart-brain Interaction during NREM Sleep Drives Sleep-dependent Memory Gains. (Advisor: Dr. Sara Mednick)
  - Dissertation Committee: Dr. Julian Thayer, Dr. Bryce Mander, Dr. Susanne Jaeggi, Dr. Greg Hickok, Dr. Aaron Bornstein
  
\newpage
- **MS in Statistics** (Sep 2018 – June 2020)
  + GPA: 3.74 / 4
  
\newpage

# Pedagogical Certificates

- [**Preparing for a Faculty Career Certificate Program**](https://github.com/pinchunc/certificates/blob/main/Pin-Chun%20Chen_PFFC%20Certificate.pdf) (Summer 2021)
- [**Mentoring Excellence Program**](https://github.com/pinchunc/certificates/blob/main/Pin-Chun%20Chen_MEP%20Certificate.pdf) (Summer 2021)
- [**Cascading Mentorship Certificate**] (March – June 2021)
- [**Public Speaking Certificate**](https://github.com/pinchunc/certificates/blob/main/Public%20Speaking%20Certificate%20-%20Pin-Chun%20Chen.pdf) (Jan – March 2021)
- **DTEI Certificate in Teaching Excellence Program** (Jul – Nov 2020)
- [**DTEI Course Design Certification Program**](https://raw.githubusercontent.com/pinchunc/certificates/013665983e1a91defe6ad0d849e24c195d680b8d/CDCP.pdf) (Aug 2020)
- [**DTEI Certificate in Remote Instruction**](https://raw.githubusercontent.com/pinchunc/certificates/013665983e1a91defe6ad0d849e24c195d680b8d/CRI.pdf) (July - Aug 2020) 



```{r out.width = "60%"}
#knitr::include_graphics(here::here("img/CRI.pdf"))
```


\newpage
\newpage

### National Chengchi University
- **B.S. in Psychology** (Sep 2013 – July 2017)
  + GPA: 4 / 4
- **B.Ed. in Education** (Sep 2013 – July 2017)
  + GPA: 4 / 4

# Awards & Honors
- 2024 Best Poster Presentation Award, MEG-UKI Conference
- 2024-2026	Junior Research Fellowship (£10K), Wolfson College, University of Oxford
- 2024-2025	Wellcome Centre for Integrative Neuroimaging Seed Grant (£15K), University of Oxford
- 2023-2025	Marie Skłodowska-Curie Postdoctoral Fellowship (€221K), Horizon Europe
- 2019-2022	Undergraduate Research Grant Recipient Advisor (3 times), UC Irvine ($2,400)
- 2022 AGS Recovery Fellowship, Associated Graduate Students, UC Irvine ($1,000)
- 2022 Spring Conference Grant Award, Associated Graduate Students, UC Irvine ($250)
- 2021 Grant Writing Fellowship, School of Social Sciences, UC Irvine ($7,000)
- 2021 Cascade Mentoring Fellow, Graduate Division, UC Irvine ($6,000)
- 2021 Jean-Claude Falmagne Research Award, UC Irvine ($3,000)
- 2021 Renée Harwick Advanced Graduate Student Award, UC Irvine ($1,000)
- 2021 Outstanding Scholarship Award, School of Social Sciences, UC Irvine ($250)
- 2021 Virtual Conference Grant Award, Associated Graduate Students, UC Irvine ($250)
- 2021 Grad Slam Semi-Finalist, Graduate Division, UC Irvine (Honorary)
- 2020 DTEI Graduate Fellow, Division of Teaching Excellence and Innovation, UC Irvine ($5,000)
- 2017 NVIDIA GPU Grant, NVIDIA Corporation ($2,000)
- 2017-2019	Government Scholarship to Study Abroad, Ministry of Education, Taiwan ($32,000)
- 2017 Honorary member of the Phi Tau Phi Scholastic Honor Society (Honorary)
- 2017 Outstanding Graduating Award (1st Class Honor), National Chengchi University, Taiwan
- 2014-2017	Student of Honor Presidential Award (6 times), National Chengchi University, Taiwan ($1,000)
- 2015 Outstanding Undergraduate Student Award, Lung Shan Temple, Taiwan ($350)
- 2015 Dr. Fa-Mi Chen Memorial Scholarship, Taiwan ($100)